\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}

### 2020-12-05 report/article.tex
added sections in article.txt (mainly in evasion)

\subsection{David Meshnick's Individual Report}

@@

We opted to compare \ilc{Fast Gradient Sign Method} (non-targeted, with one-shot and iterative implementions), \ilc{Hop Skip Jump}, \ilc{DeepFool} (and \ilc{Dynamic DeepFool} -- an extension implemented by David) together as they are all the non-targed evasion algorithm we implemented. We opted to not include \ilc{Backdoor} in this set of comparsion as it evasion attacks were done in the assumption of having a trained model, it doesn't make sense to have posioning -- which can alter the training set of a model -- to be part of the comparsion. Similarily, the two targeted extensions \ilc{FGSM} is excluded from this comparsion as in this context it is the magnitude of decrease of model \textit{accuracy} in general we care about, but not which exact label the model most classifies to.

@@

David please explain a bit on DeepFool as why it perturbed a huge amount while performed not so well, and maybe also why its $L_\infty$ is a lot higher than $L_2$.

@@

The budget analysis [\figurename{\ \ref{attack_cifar10_budget}}] comfirms our thinking as the perturbation budgets are larger acrossed the board in comparision to \textit{MINIST}. Also all other observation made from the \textit{MINIST} budget graph [\figurename{\ \ref{attack_minist_budget}}] are also true in this \textit{CIFAR-10} budget graph.

@@

\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}. David, please again summarize a bit here.

>>>>

	\subsection{David Meshnick's Individual Report}
	\subfile(individual_reports/dcm101)

@@

	We opted to compare \ilc{Fast Gradient Sign Method} (non-targeted, with one-shot and iterative implementions), \ilc{Hop Skip Jump}, \ilc{DeepFool} (and \ilc{Dynamic DeepFool} -- an extension implemented by ) together as they are all the non-targed evasion algorithm we implemented. We opted to not include \ilc{Backdoor} in this set of comparsion as it evasion attacks were done in the assumption of having a trained model, it doesn't make sense to have posioning -- which can alter the training set of a model -- to be part of the comparsion. Similarily, the two targeted extensions \ilc{FGSM} is excluded from this comparsion as in this context it is the magnitude of decrease of model \textit{accuracy} in general we care about, but not which exact label the model most classifies to.

@@

	An unexpected observation came from the DeepFool algorithm, which iterated through more perturbations than we had anticipated. This came about as a result of DeepFool's deceptively simple nature, as it is effectively a greedy search algorithm. While the function's goal is to enact the fewest possible perturbations to confidently disrupt a classifier, its descent along its gradient does not share the same efficiency. The base learning rate ended up costing a significant amount of computational resources. However, the extension David created may be a possible solution to this problem. As elaborated upon in the individual report, the Dynamic DeepFool implements a logarithmically decreasing learning rate, which improves the speed at which the algorithm approaches the class label boundary. This allowed it to have a noticeably smaller quantity of perturbation iterations, and also out performing the original DeepFool in terms of attack effectiveness on an undefended learning system.

@@

	The budget analysis [\figurename{\ \ref{attack_cifar10_budget}}] comfirms our thinking as the perturbation budgets are larger acrossed the board in comparision to \textit{MINIST}. Also all other observation made from the \textit{MINIST} budget graph [\figurename{\ \ref{attack_minist_budget}}] are also true in this \textit{CIFAR-10} budget graph.''

@@

	\ilc{DeepFool} and \ilc{D-DeepFool} have shown very similar performance across this section of experiments and their performance are considerably lacking both in terms of \textit{adversarial acc} and \textit{perturbation budget}. However, the relative-simplicity of the algorithm lends itself more easily to modification, as demonstrated by the performance gains of simply altering the learning rate of the methods gradient traversal.

	One last interesting point of comparison lies between white-box algorithms like DeepFool and black-box algorithms like One Pixel Attack. The white-box attack method had unrestrained access to the inner parameters of the victim classifier, and was typically highly effective. Meanwhile, the black-box attack could only view the inputs and outputs of the victim model, and was not as effective. However, the black-box algorithm was less computationally expensive, as well as requiring fewer parameters to act. Thus, we believe that further analysis is warranted to explore the trade-offs with regards to metrics such as computational resources and speed, between each method.
